---
title: "My R Markdown Primer"
author: "Janae Moses-Soto"
date: "2025-11-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction to R Markdown

#R Markdown is a file format for making dynamic documents in R. It is written in markdown and contains chunks of embedded R code.

##Narrative Paragraph

#This is a practice narrative paragraph. Practicing R Markdown. I do not know if I like this.

This is an inline equation: $y = mx + b$.

And here is a displayed equation, used for a linear relationship of a line:

$$ y = mx +b
$$

```{r code}
library(ggplot2)
data(mtcars)
summary(mtcars)
boxplot(mtcars)
```


## Conclusion

This is my first time using R Markdown. I can see the benefits in using it to create a html,pdf, or presentation faster with more features. However, I am not as experience using R Markdown so it's easier for me to write a plain report. The embedded code feture could be useful when you need to write a report explaining certain parts of code.